Differential Expression - MSSM-Penn-Pitt - DLPFC - Dx_Sex

### 2020-07-30 individual-cohorts/MSSM-Penn-Pitt_DLPFC_DE.Rmd
remove missing variables

# Set variable class
FactorCovariates <- c("Individual_ID", "Institution", "Reported_Gender", "LibraryBatch", "Dx", "RibozeroBatch", "FlowcellBatch")
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)

@@

# Set covariates to adjust for from model selection
adjust.covars <- c("Dx_Sex", "ageOfDeath", "RIN2", "RIN", "IntronicRate", "IntragenicRate")
random_effect <- c("Institution", "Reported_Gender")
```

>>>>

# Set variable class
FactorCovariates <- c("Individual_ID", "Institution", "LibraryBatch", "Dx_Sex", "RibozeroBatch", "FlowcellBatch")
COVARIATES[,FactorCovariates] = lapply(COVARIATES[,FactorCovariates], factor)

@@

# Set covariates to adjust for from model selection
adjust.covars <- c("Dx_Sex", "ageOfDeath", "RIN2", "RIN", "IntronicRate", "IntragenicRate")
random_effect <- c("Institution")
```
